\documentclass[sigconf,review]{acmart}

\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{epsf,picinpar}
\usepackage{varioref}
\usepackage{colortbl,multirow,hhline}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{colortbl,multirow,hhline}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[normalem]{ulem}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{balance}
\usepackage{graphicx, subfigure}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{listings}
\usepackage{framed}
\usepackage{morefloats}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{pdfpages}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{flushend}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{makecell}
\usepackage{hyperref}
\usepackage{threeparttable}
\usepackage{bm}
\renewcommand{\ttdefault}{cmr}

%\newcommand{\limit}[1]{\textcolor{red}{\noindent \ding{46}~Page limit:~#1}\\}
\newcommand{\todo}[1]{\textcolor{blue}{\ding{46}~#1}} 
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\etal}{\emph{et~al.}\xspace} 

\copyrightyear{2022}
\acmYear{2022}
\setcopyright{acmcopyright}
\acmConference[Green Lab 2022/2023]{Green Lab 2022/2023 - Vrije Universiteit Amsterdam}{September--October, 2022}{Amsterdam, The Netherlands}
\acmBooktitle{Green Lab 2022/2023 - Vrije Universiteit Amsterdam, September--October, 2022, Amsterdam (The Netherlands)}
  
\begin{document}

\title{
	Energy Consumption on Music Players:\\
 An Empirical Analysis on Spotify and YouTube Music Android Applications
}

\author{Yijing Zhou}
\affiliation{%
 \institution{2723270 \\ VU Amsterdam}
} \email{yzu710@student.vu.nll}

\author{Kunyang Gao}
\affiliation{%
 \institution{2727045 \\ VU Amsterdam}
} \email{kgo230@student.vu.nl}

\author{Han Lin}
\affiliation{%
 \institution{2724786  \\ VU Amsterdam}
} \email{h7.lin@student.vu.nl}

\author{Wenjun Liang}
\affiliation{%
 \institution{2726770  \\ VU Amsterdam}
} \email{wlg350@student.vu.nl}

\author{Ming Yue}
\affiliation{%
 \institution{2740662 \\ VU Amsterdam}
} \email{mye700@student.vu.nl}

\begin{abstract}
\noindent \textit{Context}. 
The rising popularity of music streaming platforms has immensely changed the way people consume music, especially on mobile devices. However, users are constantly challenged by the battery drain caused by massive usage of music applications.

\noindent \textit{Goal}. 
With this research we aim at conducting an empirical experiment to compare the energy consumption on two Android music streaming applications by means of analyzing how different features influence the energy consumption.  

\noindent \textit{Method}. 
The main experimental subjects are Spotify and YouTube Music. We perform a series of statistical tests on several energy-demanding factors, they are: (1) connection type (\ie Wi-Fi streaming vs. downloaded file playing), (2) sound volume (\ie low, medium, and high), and (3) audio quality (\ie low, normal, high, and very high).

\noindent \textit{Results}. 
Our findings reveal that Spotify is more energy-efficient than YouTube Music. Audio quality is the dominant factor among all three to induce higher energy consumption for both applications. Connection type influences the energy consumption differently. Sound volume is deemed as a negligible issue in terms of energy consumption. 

\noindent \textit{Conclusions}. 
 To summarize, this study provides guidance for users to extend their battery life and optimize towards energy consumption by adopting offline listening and avoiding high volume level and high audio quality. It also assists software developers to improve the energy efficiency of the application. 
\end{abstract}

\maketitle

\input{intro}
\input{related}
\input{definition}
\input{planning} 
\input{execution} 
\input{results}
\input{discussion}
\input{threats}
\input{conclusion} 

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
